Current State of Knowledge Representation Systems for Robotics

### 2011-11-21 paper.tex
Completed a bit the tables

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.7cm}p{4cm}lp{2.5cm}p{4cm}lp{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & Lemaignan (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS Ecology & Daoutis, Coradeshi, Loutfi, Saffiotti (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ReseachCyc} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

>>>>

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.7cm}p{4cm}lp{2.5cm}p{4cm}lp{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & Lemaignan (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS Ecology & Daoutis, Coradeshi, Loutfi, Saffiotti (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
DY-KNOW & Heintz, Dowerty (Linköping Univ.) & & & & & \cite{Heintz2004} \\
OMKRF & Suh et al. (Hanyang Univ.) & & & & & \cite{Suh2007} \\
GSM & Mavridis, Roy (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
 & Kollar, Tellex \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld Univ.) \\
ARMAR & Schmidt-Rohr (Karlsruhe TH) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück Univ.) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\

@@

\begin{tabular}{ll}
\hiderowcolors
{\bf Project} & {\bf Common-sense knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ReseachCyc} \\
DY-KNOW & Heitnz, Dowerty \\
OMKRF & Suh et al. (Hanyang Univ.) \\
GSM & Mavridis, Roy (MIT MediaLab) \\
 & Kollar, Tellex \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
